---
title: "Naming principles"
author: "Bruno Fischer Colonimos"
subtitle: "Conventions for making, storing and naming results, and fields of results"
abstract: |
      * Conventions for naming results in allresults (storage list , private to functions 
      initresults() result() allres()),
      * Conventions for naming fields in results, 
      * Rules for substituting fields to placeholders in text files
      * functions for doing all this
      
      ---------------
output:
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
---

Storage names and fields
========================

Structure of each results record and of the list-of-results
------------------------------------------------

```{r eval=FALSE}
allresults  # list-of-all-results = **named list** of all results, 
        |   # Privately called allresults in functions that access and modify it: initresult(), result(), allres()
        |
        |- name ... # one result set (for one analysis)
                (
                name, # supposedly, the storage name in allresults. Is it useful ??
                funname = "function name"
                varnames = c("varname1", "varname2", ...) # variable names vector
                type # result type, for rendering =============== to be added ==================
                caption, # keep ???
                numcases,  # number of non-NA cases
                summaries, # numerical summaries (quantitative variables)
                levels,  # ???????????????? what? levels of factor 1 ?
                levels2, # ???????????????? what? levels of factor 2 ?
                breaks = c(<breaks vector>), # for a continuous variable histogram and table
                closed = c("left", "right"), # for a continuous variable histogram and table
                table ,  # default table
                table1,
                table2,
                table3,
                ptable,  # printable table
                details, # additional info (mostly in table form)
                chi2,    # Chisquare test result
                anova,   # Anova test result ?
                test1,
                test2,
                test3,
                plot, # default plot
                plot1,
                plot2,
                plot3 
                        )
        |
        |- name ... # one result
        |
        |- name ... # one result
                
```




Functions relative to results sets and list-of-results 
-----------------------------------------------------

* initresult() -- initializes list-of-results and create accessor functions
        # call:
        # resultfuns <- initresult()
        # result <- resultfuns[[1]]
        # allres <- resultfuns[[2]]
* make.result() -- makes a result set
* result() -- stores or retrieves a result set: 
        # result("name", value) or
        # result("name")
* allres() -- returns the list of all results
* allresnames() -- # get list of names from the list of results (finds and returns the "external" storage names)






---------------------------------------------------------------------------------------------------------



Rendering
=========


Rendering patterns in a special subdirectory

naming : name_text.Rmd 

association with result type : correspondence table (or pairlist)

function for associating a result type  with a rendering pattern

render(type,  pattern) -- modify the assoc list.


standard functions: type = funname, pattern = funname_test.Rmd.

custom functions: type = customname, pattern list = vector



OR: 2 associations

result type --> pattern name
pattern name --> vector of text line chunk names


plus, a simplified way:

result type --> vector of line chunks names(for custom result types)


examples:


```{r eval=FALSE}

line_chunks <- list(
        # typical function-rendering texts
        "cat1" = list (......), # list of lines
        "num1d"= list (......), # list of lines
        ......
        # "lego-like"" line chunks, to allow custom rendering
        "_xx_title" = list (......), # list of lines for title rendering
        "_xx_plot1" = list (......), # list of lines for plot display
        "_xx_ptable"= list (......), # list of lines for table display
        .......
        )

```









---------------------------------------------------------------------------------------------------------

Old
====


2 variables
-----------

* name = paste( variable1 , separator, variable2)



To do 1
===========

* protection against overwriting a result by using the same name

* naming system

* how it should be:

res, res2 are analysis results
nam is its storage name
nam2

# initial storage
result(nam, res) # stores res in the result list, under the name nam

# overwrite protection
result(nam, res) # ==> should :
a) lookup nam in the list. If it is already used, change nam into nam1 and try again, until it works
b) issue a warning

# overwrite protection 2: intentional overwrite
result(nam, res, overwrite = TRUE) # disables overwrite protection

# updating a stored result
result.update(name , compname, newvalue) {
                res <- update.result(result(name), compname, newvalue) # updates component
                result(name, res, overwrite = TRUE) # store again updated result res.
}

update.result(res, compname, newvalue)
# check that compname is valid and then res[compname] <- newvalue and return res


# use that for storage of result : make name, then record storage name in the result ?


To do 2
============

# make a storage name with a vector of variables

make.a.name(varvect) {
        paste(varvect, sep = sfdefaults("varsep"))
}

# recording function


To do 3
============

Change the text files. review variable names there !
* name of chunk
* name of variable (s)
* name of stored result
* etc.


