---
title: "TD 1 stats"
author: "Bruno Fischer Colonimos"
output:
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
subtitle: "Variable par variable, à plat"
---

```{r init, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, warning=FALSE)
# opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5)
options(digits = 2, scipen = 7)
# width + heights figures constants
dkfigwidth <- 5
dkfigheight <- 5
lkfigwidth <- 8
lkfigheight <- 7
```


```{r morecode, include=FALSE, warning=FALSE}
# More code
# ---------
source("standardfunctionsV10.R")
```




```{r data_in}

# load data
df <- read.csv2(file.path("data", "1_1.csv"))
# make factor with int
df$arrondissement <- factor(df$arrondissement)
colnames(df) <- c("client.no" , "arrondissement", "genre" , "age",
                  "montant.depense", "nombre.de.visites", "riz.complet", 
                  "tablettes.chocolat")


```




Analyse à plat
=================

```{r res_store,results="hide"}
# Storing results
# initialization
initresult <- function() {
        allresults <- list(whatsit = "resultlist") # encapsulated list of results
        function(rname, rval) {
        if (missing(rval)) {
                allresults[[rname]]
        } else {
                allresults[[rname]] <<- rval
                rname
        }
}
}


# modifier and accessor function
result <- initresult

```


```{r listtaf}

getvars <- function(dframe) {
        cl <- sapply(dframe, function(col) class(col))
        ddf <- data.frame( names = colnames(dframe), 
                    types = cl )
        ddf
        # cl
}

cl <- getvars(df)

d <- data.frame(colnames(df), cl)






todo <- unlist(lapply(colnames(df),
              function(x) {
                      paste0("result(",
                             "'", x, "'", ",  ", ")" )}
              ))

cat(todo, sep="\n")

```


```{r makeresults, results="hide"}

# result('client.no', 
#        ) 

result('arrondissement',  
       cat1(df, 'arrondissement')) 

result('genre', cat1(df, 'genre') ) 

result('age', 
       num1c(df, "age", breaks = seq(20, 80, by=10), closed = "left" 
             # bins = "nclass.Sturges"
             ) )
result('age_d', num1d(df, "age") )

result('montant.depense', 
       num1c(df, "montant.depense", breaks = seq(40, 240, by = 20),
             closed = "left" 
             # bins = "nclass.Sturges"
             ) ) 

result('nombre.de.visites', num1d(df, "nombre.de.visites") ) 

result('riz.complet', cat1(df, 'riz.complet') ) 

result('tablettes.chocolat', 
       num1d(df, "tablettes.chocolat") )

```


```{r arr1}
var <- "arrondissement"
res <- result(var)
```

variable : `r res$name`, (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentations graphiques

```{r}
res$plot
res$plot1
```


-------------------------------------

```{r genre1}
var <- "genre"
res <- result(var)
```

variable : `r res$name`, (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentations graphiques

```{r}
res$plot
res$plot1
```



-------------------------------------

```{r riz1}
# colnames(df)
var <- "riz.complet"
res <- result(var)
```

variable : `r res$name`, (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentations graphiques

```{r}
res$plot
res$plot1
```


-------------------------------------

```{r}
# colnames(df)
var <- "age_d"
res <- result(var)
```

variable : `r res$name`, (variable discrète) (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)

kable(t(as.data.frame(res$summaries)))
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentation graphiques

```{r}
res$plot
```

-------------------------------------

```{r}
# colnames(df)
var <- "age"
res <- result(var)
```

variable : `r res$name`, (variable continue) (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)

kable(t(as.data.frame(res$summaries)))
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentation graphique

```{r}
res$plot
```



-------------------------------------

```{r}
# colnames(df)
var <- "montant.depense"
res <- result(var)
```

variable : `r res$name`, (variable continue) (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)

kable(t(as.data.frame(res$summaries)))
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentation graphique

```{r}
ggplot(df, aes(x=1,y=montant.depense)) + geom_boxplot()
res$plot
```



-------------------------------------

```{r}
# colnames(df)
var <- "nombre.de.visites"
res <- result(var)
```

variable : `r res$name`, (variable discrète) (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)

kable(t(as.data.frame(res$summaries)))
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentation graphiques

```{r}
res$plot
```



-------------------------------------

```{r}
# colnames(df)
var <- "tablettes.chocolat"
res <- result(var)
```

variable : `r res$name`, (variable discrète) (effectif = `r res$numcases`)
------------------------------------------------------

```{r}
kable(res$ptable)

kable(t(as.data.frame(res$summaries)))
```

Test du chi2 (équirépartition) : `r res$chi2$test1$method` : p-valeur `r res$chi2$test1$p.value`

Représentation graphiques

```{r}
res$plot
```






